Online Multiclass Linear Classification with Bandit Feedback

### 2019-01-16 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
Add reference to binary perceptron

%The algorithm is stated as
% and
%the mistake upper bound is stated as.

The idea behind Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
 is to use $K$ copies of the \textsc{Binary
Perceptron} algorithm,
\chicheng{Shall we define the binary Perceptron algorithm?}
where each copy corresponds to a class. At each timestep $t$, upon seeing
example $x_t$,
copy $i$ makes a binary prediction on whether $x_t$ belongs to
class $i$ or not. If at least one copy makes a positive prediction, the
algorithm chooses its prediction as one of the classes corresponding to a
positive prediction. If all copies make negative predictions, the algorithms
makes a prediction uniformly at random.

>>>>

The idea behind
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} is
to use $K$ copies of the \textsc{Binary Perceptron} algorithm; see e.g.
\citet[Section 3.3.1]{Shalev-Shwartz-2012}. Each copy corresponds to one of the
classes. At each timestep $t$, upon seeing example $x_t$, copy $i$ makes a
binary prediction on whether $x_t$ belongs to class $i$ or not. If at least one
copy makes a positive prediction, the algorithm chooses its prediction as one of
the classes corresponding to a positive prediction. If all copies make negative
predictions, the algorithms makes a prediction uniformly at random.
